---
title: "STATEC Workshop - R Session 1"
author: "Hamed Vaheb"
date: "25/10/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
library(ggplot2)
library(broom)
library(reshape2)
library(readr)
library(readxl)
#library(Ecdat)
library(janitor)
library(plm)
library(pwt9)
library(quarto)
library(renv)
library(shiny)
library(targets)
library(testthat)
library(tidyverse)
library(tibble)
library(usethis)
library(rio)
library(lubridate)
library(purrr)
```
We import data

# Prepare

First of all we import the dataset:
```{r}
mtcars <- rio::import("mtcars.csv")
mtcars_dta <- rio::import("mtcars.dta")
mccars_sas <- rio::import("mtcars.sas7bdat")

multi_xlsx <- rio::import_list("multi.xlsx")

#paths <- Sys.glob("unemployment/*.csv")
#unemployment <- rio:: import_list(paths, rbind=True)


urls <- c("https://raw.githubusercontent.com/b-rodrigues/modern_R/master/datasets/unemployment/unemp_2013.csv", 
	  "https://raw.githubusercontent.com/b-rodrigues/modern_R/master/datasets/unemployment/unemp_2014.csv", 
	  "https://raw.githubusercontent.com/b-rodrigues/modern_R/master/datasets/unemployment/unemp_2015.csv", 
	  "https://raw.githubusercontent.com/b-rodrigues/modern_R/master/datasets/unemployment/unemp_2016.csv")

## seting rbind == TRUE adds a column in which source the row (from which file) 
unemployment <- rio::import_list(urls, rbind=TRUE)

#unemployment <- lapply(urls, read.csv) %>% dplyr::bind_rows

```


```{r}
starwars %>%
  filter(!is.na(hair_color)) %>%
  group_by(sex) %>%
  summarise(mean_mass = mean(mass, na.rm=TRUE))
  
```

```{r}
10000000000
print(nchar(10000000000))
print(nchar("10000000000"))

```

```{r}
starwars %>%
  filter(gender == "masculine") %>%
  group_by(sex) %>%
  summarise(mean_height = mean(height, na.rm = TRUE))
```



```{r}
unemp <- unemployment %>% 
  janitor::clean_names() %>% 
  filter(commune %in% c("Luxembourg", "Esch-sur-Alzette", "Wiltz")) %>% 
  group_by(commune) %>%
  nest() %>% 
  mutate(plot = map2(.x = data, .y = commune, ~ggplot(data = .x) +
                       theme_minimal() +
                       geom_line(aes(year, unemployment_rate_in_percent, group = 1)) +
                       labs(title = paste("Unemployment in", .y))),
         saved_plots = map2(.x = commune,
                            .y = plot,
                            ~ggsave(paste0("plot_for_", .x, ".pdf"),
                                         .y)))

```


r2u is to avoid 

https://github.com/eddelbuettel/r2u


Pure function: shouldn't depend on something outside of its scope
Ex: shouldn't require seed before it


Functional programming is declarative, as we state what we want

library(withr) allows to rnorm with seed


Running function with side effect of seed

What we need is a wrapper for function os that it doesn't rely on anything from outside.


if inside your function you load library, it is not pure
because it changes the global state.

higher-order function: takes or returns functions

purrr:possibly
purrr::quietly


with_options
to change parameters for functions
```{r}
map_dbl(c(1,2,3), sqrt)

#reduce(c(1,2,3))
```

Functional code is very easy to parallelize
and also use map and reduce in parallel
Look here:
https://www.brodrigues.co/blog/2019-10-05-parallel_maxlik/

If we use map_future from the package furr
we can replace it with any map function to run the map in parallel.

furrr::feature_map

dplyr:: select(mtcars, am)


ls(mtcars)



simple_function:
don't evaluate it immediately, wait to diffuse it later,


enquo: diffuses col_name
!!col_name: (!!) now use it in context of global 


colnames(iris)
ls(iris)

simple_function(iris, Species)

Species 

"Species" when I run it doesn't exist , but simple_function(iris, Species) then exists


```{r}
simple_function <- function(dataset, col_name){
  #print(col_name)
  col_name <- enquo(col_name)
  #print(col_name)
  dataset %>%
    group_by(!!col_name) %>%
    summarise(mean_mpg = mean(mpg))
}


simple_function(mtcars, mpg)
```
```{r}
a <- list(1, "a", 4, 5)
safe_sqrt <- safely(sqrt)
result_a <- map(a, safe_sqrt)
p_sqrt <- possibly(sqrt, otherwise = NULL)
map(a, p_sqrt)
```
tidymodels.org/start/models

ssh -T git@github.com
